### 2019-09-10 reports/iclr/iclr2020_conference.tex
Add ICLR template

\documentclass{article} % For LaTeX2e
\usepackage{iclr2020_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}

\title{Formatting Instructions for ICLR 2020 \\ Conference Submissions}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.  Funding acknowledgements go at the end of the paper.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213, USA \\
\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
\And
Ji Q. Ren \& Yevgeny LeNet \\
Department of Computational Neuroscience \\
University of the Witwatersrand \\
Joburg, South Africa \\
\texttt{\{robot,net\}@wits.ac.za} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}

\maketitle

\begin{abstract}
The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
The word \textsc{Abstract} must be centered, in small caps, and in point size 12. Two
line spaces precede the abstract. The abstract must be limited to one
paragraph.
\end{abstract}

\section{Submission of conference papers to ICLR 2020}

ICLR requires electronic submissions, processed by
\url{https://openreview.net/}. See ICLR's website for more instructions.

If your paper is ultimately accepted, the statement {\tt
  {\textbackslash}iclrfinalcopy} should be inserted to adjust the
format to the camera ready requirements.

The format for the submissions is a variant of the NIPS format.
Please read carefully the instructions below, and follow them
faithfully.

\subsection{Style}

Papers to be submitted to ICLR 2020 must be prepared according to the
instructions presented here.

%% Please note that we have introduced automatic line number generation
%% into the style file for \LaTeXe. This is to help reviewers
%% refer to specific lines of the paper when they make their comments. Please do
%% NOT refer to these line numbers in your paper as they will be removed from the
%% style file for the final version of accepted papers.

Authors are required to use the ICLR \LaTeX{} style files obtainable at the
ICLR website. Please make sure you use the current files and
not previous versions. Tweaking the style files may be grounds for rejection.

\subsection{Retrieval of style files}

The style files for ICLR and other conference information are available online at:
\begin{center}
   \url{http://www.iclr.cc/}
\end{center}
The file \verb+iclr2020_conference.pdf+ contains these
instructions and illustrates the
various formatting requirements your ICLR paper must satisfy.
Submissions must be made using \LaTeX{} and the style files
\verb+iclr2020_conference.sty+ and \verb+iclr2020_conference.bst+ (to be used with \LaTeX{}2e). The file
\verb+iclr2020_conference.tex+ may be used as a ``shell'' for writing your paper. All you
have to do is replace the author, title, abstract, and text of the paper with
your own.

The formatting instructions contained in these style files are summarized in
sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).
Use 10~point type with a vertical spacing of 11~points. Times New Roman is the
preferred typeface throughout. Paragraphs are separated by 1/2~line space,
with no indentation.

Paper title is 17~point, in small caps and left-aligned.
All pages should start at 1~inch (6~picas) from the top of the page.

Authors' names are
set in boldface, and each name is placed above its corresponding
address. The lead author's name is to be listed first, and
the co-authors' names are set to follow. Authors sharing the
same address can be on the same line.

Please pay special attention to the instructions in section \ref{others}
regarding figures, tables, acknowledgments, and references.

The recommended paper length is 8 pages, with unlimited additional pages for
citations.  There will be a strict upper limit of 10 pages for the main text.
Reviewers will be instructed to apply a higher standard to papers in excess of 8
pages.  Authors may use as many pages of appendices (after the bibliography) as
they wish, but reviewers are not required to read these.

\section{Headings: first level}
\label{headings}

First level headings are in small caps,
flush left and in point size 12. One line space before the first level
heading and 1/2~line space after the first level heading.

\subsection{Headings: second level}

Second level headings are in small caps,
flush left and in point size 10. One line space before the second level
heading and 1/2~line space after the second level heading.

\subsubsection{Headings: third level}

Third level headings are in small caps,
flush left and in point size 10. One line space before the third level
heading and 1/2~line space after the third level heading.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone, regardless of the formatter being used.

\subsection{Citations within the text}

Citations within the text should be based on the \texttt{natbib} package
and include the authors' last names and year (with the ``et~al.'' construct
for more than two authors). When the authors or the publication are
included in the sentence, the citation should not be in parenthesis using \verb|\citet{}| (as
in ``See \citet{Hinton06} for more information.''). Otherwise, the citation
should be in parenthesis using \verb|\citep{}| (as in ``Deep learning shows promise to make progress 
towards AI~\citep{Bengio+chapter2007}.'').

The corresponding references are to be listed in alphabetical order of
authors, in the \textsc{References} section. As to the format of the
references themselves, any style is acceptable as long as it is used
consistently.

\subsection{Footnotes}

Indicate footnotes with a number\footnote{Sample of the first footnote} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches
(12~picas).\footnote{Sample of the second footnote}

\subsection{Figures}

All artwork must be neat, clean, and legible. Lines should be dark
enough for purposes of reproduction; art work should not be
hand-drawn. The figure number and caption always appear after the
figure. Place one line space before the figure caption, and one line
space after the figure. The figure caption is lower case (except for
first word and proper nouns); figures are numbered consecutively.

Make sure the figure caption does not get separated from the figure.
Leave sufficient space to avoid splitting the figure and figure caption.

You may use color figures.
However, it is best for the
figure captions and the paper body to make sense if the paper is printed
either in black/white or in color.
\begin{figure}[h]
\begin{center}
%\framebox[4.0in]{$\;$}
\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
\end{center}
\caption{Sample figure caption.}
\end{figure}

\subsection{Tables}

All tables must be centered, neat, clean and legible. Do not use hand-drawn
tables. The table number and title always appear before the table. See
Table~\ref{sample-table}.

Place one line space before the table title, one line space after the table
title, and one line space after the table. The table title must be lower case
(except for first word and proper nouns); tables are numbered consecutively.

\begin{table}[t]
\caption{Sample table title}
\label{sample-table}
\begin{center}
\begin{tabular}{ll}
\multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION}
\\ \hline \\
Dendrite         &Input terminal \\
Axon             &Output terminal \\
Soma             &Cell body (contains cell nucleus) \\
\end{tabular}
\end{center}
\end{table}

\section{Default Notation}

In an attempt to encourage standardized notation, we have included the
notation file from the textbook, \textit{Deep Learning}
\cite{goodfellow2016deep} available at
\url{https://github.com/goodfeli/dlbook_notation/}.  Use of this style
is not required and can be disabled by commenting out
\texttt{math\_commands.tex}.

\centerline{\bf Numbers and Arrays}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1in}p{3.25in}}
$\displaystyle a$ & A scalar (integer or real)\\
$\displaystyle \va$ & A vector\\
$\displaystyle \mA$ & A matrix\\
$\displaystyle \tA$ & A tensor\\
$\displaystyle \mI_n$ & Identity matrix with $n$ rows and $n$ columns\\
$\displaystyle \mI$ & Identity matrix with dimensionality implied by context\\
$\displaystyle \ve^{(i)}$ & Standard basis vector $[0,\dots,0,1,0,\dots,0]$ with a 1 at position $i$\\
$\displaystyle \text{diag}(\va)$ & A square, diagonal matrix with diagonal entries given by $\va$\\
$\displaystyle \ra$ & A scalar random variable\\
$\displaystyle \rva$ & A vector-valued random variable\\
$\displaystyle \rmA$ & A matrix-valued random variable\\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Sets and Graphs}
\bgroup
\def\arraystretch{1.5}

\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle \sA$ & A set\\
$\displaystyle \R$ & The set of real numbers \\
$\displaystyle \{0, 1\}$ & The set containing 0 and 1 \\
$\displaystyle \{0, 1, \dots, n \}$ & The set of all integers between $0$ and $n$\\
$\displaystyle [a, b]$ & The real interval including $a$ and $b$\\
$\displaystyle (a, b]$ & The real interval excluding $a$ but including $b$\\
$\displaystyle \sA \backslash \sB$ & Set subtraction, i.e., the set containing the elements of $\sA$ that are not in $\sB$\\
$\displaystyle \gG$ & A graph\\
$\displaystyle \parents_\gG(\ervx_i)$ & The parents of $\ervx_i$ in $\gG$
\end{tabular}
\vspace{0.25cm}

\centerline{\bf Indexing}
\bgroup
\def\arraystretch{1.5}

\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle \eva_i$ & Element $i$ of vector $\va$, with indexing starting at 1 \\
$\displaystyle \eva_{-i}$ & All elements of vector $\va$ except for element $i$ \\
$\displaystyle \emA_{i,j}$ & Element $i, j$ of matrix $\mA$ \\
$\displaystyle \mA_{i, :}$ & Row $i$ of matrix $\mA$ \\
$\displaystyle \mA_{:, i}$ & Column $i$ of matrix $\mA$ \\
$\displaystyle \etA_{i, j, k}$ & Element $(i, j, k)$ of a 3-D tensor $\tA$\\
$\displaystyle \tA_{:, :, i}$ & 2-D slice of a 3-D tensor\\
$\displaystyle \erva_i$ & Element $i$ of the random vector $\rva$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Calculus}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
% NOTE: the [2ex] on the next line adds extra height to that row of the table.
% Without that command, the fraction on the first line is too tall and collides
% with the fraction on the second line.
$\displaystyle\frac{d y} {d x}$ & Derivative of $y$ with respect to $x$\\ [2ex]
$\displaystyle \frac{\partial y} {\partial x} $ & Partial derivative of $y$ with respect to $x$ \\
$\displaystyle \nabla_\vx y $ & Gradient of $y$ with respect to $\vx$ \\
$\displaystyle \nabla_\mX y $ & Matrix derivatives of $y$ with respect to $\mX$ \\
$\displaystyle \nabla_\tX y $ & Tensor containing derivatives of $y$ with respect to $\tX$ \\
$\displaystyle \frac{\partial f}{\partial \vx} $ & Jacobian matrix $\mJ \in \R^{m\times n}$ of $f: \R^n \rightarrow \R^m$\\
$\displaystyle \nabla_\vx^2 f(\vx)\text{ or }\mH( f)(\vx)$ & The Hessian matrix of $f$ at input point $\vx$\\
$\displaystyle \int f(\vx) d\vx $ & Definite integral over the entire domain of $\vx$ \\
$\displaystyle \int_\sS f(\vx) d\vx$ & Definite integral with respect to $\vx$ over the set $\sS$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Probability and Information Theory}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle P(\ra)$ & A probability distribution over a discrete variable\\
$\displaystyle p(\ra)$ & A probability distribution over a continuous variable, or over
a variable whose type has not been specified\\
$\displaystyle \ra \sim P$ & Random variable $\ra$ has distribution $P$\\% so thing on left of \sim should always be a random variable, with name beginning with \r
$\displaystyle  \E_{\rx\sim P} [ f(x) ]\text{ or } \E f(x)$ & Expectation of $f(x)$ with respect to $P(\rx)$ \\
$\displaystyle \Var(f(x)) $ &  Variance of $f(x)$ under $P(\rx)$ \\
$\displaystyle \Cov(f(x),g(x)) $ & Covariance of $f(x)$ and $g(x)$ under $P(\rx)$\\
$\displaystyle H(\rx) $ & Shannon entropy of the random variable $\rx$\\
$\displaystyle \KL ( P \Vert Q ) $ & Kullback-Leibler divergence of P and Q \\
$\displaystyle \mathcal{N} ( \vx ; \vmu , \mSigma)$ & Gaussian distribution %
over $\vx$ with mean $\vmu$ and covariance $\mSigma$ \\
\end{tabular}
\egroup
\vspace{0.25cm}

\centerline{\bf Functions}
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{p{1.25in}p{3.25in}}
$\displaystyle f: \sA \rightarrow \sB$ & The function $f$ with domain $\sA$ and range $\sB$\\
$\displaystyle f \circ g $ & Composition of the functions $f$ and $g$ \\
  $\displaystyle f(\vx ; \vtheta) $ & A function of $\vx$ parametrized by $\vtheta$.
  (Sometimes we write $f(\vx)$ and omit the argument $\vtheta$ to lighten notation) \\
$\displaystyle \log x$ & Natural logarithm of $x$ \\
$\displaystyle \sigma(x)$ & Logistic sigmoid, $\displaystyle \frac{1} {1 + \exp(-x)}$ \\
$\displaystyle \zeta(x)$ & Softplus, $\log(1 + \exp(x))$ \\
$\displaystyle || \vx ||_p $ & $\normlp$ norm of $\vx$ \\
$\displaystyle || \vx || $ & $\normltwo$ norm of $\vx$ \\
$\displaystyle x^+$ & Positive part of $x$, i.e., $\max(0,x)$\\
$\displaystyle \1_\mathrm{condition}$ & is 1 if the condition is true, 0 otherwise\\
\end{tabular}
\egroup
\vspace{0.25cm}

\section{Final instructions}
Do not change any aspects of the formatting parameters in the style files.
In particular, do not modify the width or length of the rectangle the text
should fit into, and do not change font sizes (except perhaps in the
\textsc{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PostScript or PDF files}

Please prepare PostScript or PDF files with paper size ``US Letter'', and
not, for example, ``A4''. The -t
letter option on dvips will produce US Letter files.

Consider directly generating PDF files using \verb+pdflatex+
(especially if you are a MiKTeX user).
PDF figures must be substituted for EPS figures, however.

Otherwise, please generate your PostScript and PDF files with the following commands:
\begin{verbatim}
dvips mypaper.dvi -t letter -Ppdf -G0 -o mypaper.ps
ps2pdf mypaper.ps mypaper.pdf
\end{verbatim}

\subsection{Margins in LaTeX}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+
from the graphicx package. Always specify the figure width as a multiple of
the line width as in the example below using .eps graphics
\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.eps}
\end{verbatim}
or % Apr 2009 addition
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
for .pdf graphics.
See section~4.4 in the graphics bundle documentation (\url{http://www.ctan.org/tex-archive/macros/latex/required/graphics/grfguide.ps})

A number of width problems arise when LaTeX cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command.

\subsubsection*{Author Contributions}
If you'd like to, you may include  a section for author contributions as is done
in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}
Use unnumbered third level headings for the acknowledgments. All
acknowledgments, including those to funding agencies, go at the end of the paper.

\bibliography{iclr2020_conference}
\bibliographystyle{iclr2020_conference}

\appendix
\section{Appendix}
You may include other additional sections here.

\end{document}

### 2019-09-10 reports/iclr/paper.tex
Add blank paper

--- 2019-09-10 reports/iclr/iclr2020_conference.tex
@@
 
-\section{Submission of conference papers to ICLR 2020}
-
-ICLR requires electronic submissions, processed by
-\url{https://openreview.net/}. See ICLR's website for more instructions.
-
-If your paper is ultimately accepted, the statement {\tt
-  {\textbackslash}iclrfinalcopy} should be inserted to adjust the
-format to the camera ready requirements.
-
-The format for the submissions is a variant of the NIPS format.
-Please read carefully the instructions below, and follow them
-faithfully.
-
-\subsection{Style}
-
-Papers to be submitted to ICLR 2020 must be prepared according to the
-instructions presented here.
-
-%% Please note that we have introduced automatic line number generation
-%% into the style file for \LaTeXe. This is to help reviewers
-%% refer to specific lines of the paper when they make their comments. Please do
-%% NOT refer to these line numbers in your paper as they will be removed from the
-%% style file for the final version of accepted papers.
-
-Authors are required to use the ICLR \LaTeX{} style files obtainable at the
-ICLR website. Please make sure you use the current files and
-not previous versions. Tweaking the style files may be grounds for rejection.
-
-\subsection{Retrieval of style files}
-
-The style files for ICLR and other conference information are available online at:
-\begin{center}
-   \url{http://www.iclr.cc/}
-\end{center}
-The file \verb+iclr2020_conference.pdf+ contains these
-instructions and illustrates the
-various formatting requirements your ICLR paper must satisfy.
-Submissions must be made using \LaTeX{} and the style files
-\verb+iclr2020_conference.sty+ and \verb+iclr2020_conference.bst+ (to be used with \LaTeX{}2e). The file
-\verb+iclr2020_conference.tex+ may be used as a ``shell'' for writing your paper. All you
-have to do is replace the author, title, abstract, and text of the paper with
-your own.
-
-The formatting instructions contained in these style files are summarized in
-sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.
-
-\section{General formatting instructions}
-\label{gen_inst}
-
-The text must be confined within a rectangle 5.5~inches (33~picas) wide and
-9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).
-Use 10~point type with a vertical spacing of 11~points. Times New Roman is the
-preferred typeface throughout. Paragraphs are separated by 1/2~line space,
-with no indentation.
-
-Paper title is 17~point, in small caps and left-aligned.
-All pages should start at 1~inch (6~picas) from the top of the page.
-
-Authors' names are
-set in boldface, and each name is placed above its corresponding
-address. The lead author's name is to be listed first, and
-the co-authors' names are set to follow. Authors sharing the
-same address can be on the same line.
-
-Please pay special attention to the instructions in section \ref{others}
-regarding figures, tables, acknowledgments, and references.
-
-The recommended paper length is 8 pages, with unlimited additional pages for
-citations.  There will be a strict upper limit of 10 pages for the main text.
-Reviewers will be instructed to apply a higher standard to papers in excess of 8
-pages.  Authors may use as many pages of appendices (after the bibliography) as
-they wish, but reviewers are not required to read these.
-
-\section{Headings: first level}
-\label{headings}
-
-First level headings are in small caps,
-flush left and in point size 12. One line space before the first level
-heading and 1/2~line space after the first level heading.
-
-\subsection{Headings: second level}
-
-Second level headings are in small caps,
-flush left and in point size 10. One line space before the second level
-heading and 1/2~line space after the second level heading.
-
-\subsubsection{Headings: third level}
-
-Third level headings are in small caps,
-flush left and in point size 10. One line space before the third level
-heading and 1/2~line space after the third level heading.
-
-\section{Citations, figures, tables, references}
-\label{others}
-
-These instructions apply to everyone, regardless of the formatter being used.
-
-\subsection{Citations within the text}
-
-Citations within the text should be based on the \texttt{natbib} package
-and include the authors' last names and year (with the ``et~al.'' construct
-for more than two authors). When the authors or the publication are
-included in the sentence, the citation should not be in parenthesis using \verb|\citet{}| (as
-in ``See \citet{Hinton06} for more information.''). Otherwise, the citation
-should be in parenthesis using \verb|\citep{}| (as in ``Deep learning shows promise to make progress 
-towards AI~\citep{Bengio+chapter2007}.'').
-
-The corresponding references are to be listed in alphabetical order of
-authors, in the \textsc{References} section. As to the format of the
-references themselves, any style is acceptable as long as it is used
-consistently.
-
-\subsection{Footnotes}
-
-Indicate footnotes with a number\footnote{Sample of the first footnote} in the
-text. Place the footnotes at the bottom of the page on which they appear.
-Precede the footnote with a horizontal rule of 2~inches
-(12~picas).\footnote{Sample of the second footnote}
-
-\subsection{Figures}
-
-All artwork must be neat, clean, and legible. Lines should be dark
-enough for purposes of reproduction; art work should not be
-hand-drawn. The figure number and caption always appear after the
-figure. Place one line space before the figure caption, and one line
-space after the figure. The figure caption is lower case (except for
-first word and proper nouns); figures are numbered consecutively.
-
-Make sure the figure caption does not get separated from the figure.
-Leave sufficient space to avoid splitting the figure and figure caption.
-
-You may use color figures.
-However, it is best for the
-figure captions and the paper body to make sense if the paper is printed
-either in black/white or in color.
-\begin{figure}[h]
-\begin{center}
-%\framebox[4.0in]{$\;$}
-\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
-\end{center}
-\caption{Sample figure caption.}
-\end{figure}
-
-\subsection{Tables}
-
-All tables must be centered, neat, clean and legible. Do not use hand-drawn
-tables. The table number and title always appear before the table. See
-Table~\ref{sample-table}.
-
-Place one line space before the table title, one line space after the table
-title, and one line space after the table. The table title must be lower case
-(except for first word and proper nouns); tables are numbered consecutively.
-
-\begin{table}[t]
-\caption{Sample table title}
-\label{sample-table}
-\begin{center}
-\begin{tabular}{ll}
-\multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION}
-\\ \hline \\
-Dendrite         &Input terminal \\
-Axon             &Output terminal \\
-Soma             &Cell body (contains cell nucleus) \\
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Default Notation}
-
-In an attempt to encourage standardized notation, we have included the
-notation file from the textbook, \textit{Deep Learning}
-\cite{goodfellow2016deep} available at
-\url{https://github.com/goodfeli/dlbook_notation/}.  Use of this style
-is not required and can be disabled by commenting out
-\texttt{math\_commands.tex}.
-
-\centerline{\bf Numbers and Arrays}
-\bgroup
-\def\arraystretch{1.5}
-\begin{tabular}{p{1in}p{3.25in}}
-$\displaystyle a$ & A scalar (integer or real)\\
-$\displaystyle \va$ & A vector\\
-$\displaystyle \mA$ & A matrix\\
-$\displaystyle \tA$ & A tensor\\
-$\displaystyle \mI_n$ & Identity matrix with $n$ rows and $n$ columns\\
-$\displaystyle \mI$ & Identity matrix with dimensionality implied by context\\
-$\displaystyle \ve^{(i)}$ & Standard basis vector $[0,\dots,0,1,0,\dots,0]$ with a 1 at position $i$\\
-$\displaystyle \text{diag}(\va)$ & A square, diagonal matrix with diagonal entries given by $\va$\\
-$\displaystyle \ra$ & A scalar random variable\\
-$\displaystyle \rva$ & A vector-valued random variable\\
-$\displaystyle \rmA$ & A matrix-valued random variable\\
-\end{tabular}
-\egroup
-\vspace{0.25cm}
-
-\centerline{\bf Sets and Graphs}
-\bgroup
-\def\arraystretch{1.5}
-
-\begin{tabular}{p{1.25in}p{3.25in}}
-$\displaystyle \sA$ & A set\\
-$\displaystyle \R$ & The set of real numbers \\
-$\displaystyle \{0, 1\}$ & The set containing 0 and 1 \\
-$\displaystyle \{0, 1, \dots, n \}$ & The set of all integers between $0$ and $n$\\
-$\displaystyle [a, b]$ & The real interval including $a$ and $b$\\
-$\displaystyle (a, b]$ & The real interval excluding $a$ but including $b$\\
-$\displaystyle \sA \backslash \sB$ & Set subtraction, i.e., the set containing the elements of $\sA$ that are not in $\sB$\\
-$\displaystyle \gG$ & A graph\\
-$\displaystyle \parents_\gG(\ervx_i)$ & The parents of $\ervx_i$ in $\gG$
-\end{tabular}
-\vspace{0.25cm}
-
-\centerline{\bf Indexing}
-\bgroup
-\def\arraystretch{1.5}
-
-\begin{tabular}{p{1.25in}p{3.25in}}
-$\displaystyle \eva_i$ & Element $i$ of vector $\va$, with indexing starting at 1 \\
-$\displaystyle \eva_{-i}$ & All elements of vector $\va$ except for element $i$ \\
-$\displaystyle \emA_{i,j}$ & Element $i, j$ of matrix $\mA$ \\
-$\displaystyle \mA_{i, :}$ & Row $i$ of matrix $\mA$ \\
-$\displaystyle \mA_{:, i}$ & Column $i$ of matrix $\mA$ \\
-$\displaystyle \etA_{i, j, k}$ & Element $(i, j, k)$ of a 3-D tensor $\tA$\\
-$\displaystyle \tA_{:, :, i}$ & 2-D slice of a 3-D tensor\\
-$\displaystyle \erva_i$ & Element $i$ of the random vector $\rva$ \\
-\end{tabular}
-\egroup
-\vspace{0.25cm}
-
-\centerline{\bf Calculus}
-\bgroup
-\def\arraystretch{1.5}
-\begin{tabular}{p{1.25in}p{3.25in}}
-% NOTE: the [2ex] on the next line adds extra height to that row of the table.
-% Without that command, the fraction on the first line is too tall and collides
-% with the fraction on the second line.
-$\displaystyle\frac{d y} {d x}$ & Derivative of $y$ with respect to $x$\\ [2ex]
-$\displaystyle \frac{\partial y} {\partial x} $ & Partial derivative of $y$ with respect to $x$ \\
-$\displaystyle \nabla_\vx y $ & Gradient of $y$ with respect to $\vx$ \\
-$\displaystyle \nabla_\mX y $ & Matrix derivatives of $y$ with respect to $\mX$ \\
-$\displaystyle \nabla_\tX y $ & Tensor containing derivatives of $y$ with respect to $\tX$ \\
-$\displaystyle \frac{\partial f}{\partial \vx} $ & Jacobian matrix $\mJ \in \R^{m\times n}$ of $f: \R^n \rightarrow \R^m$\\
-$\displaystyle \nabla_\vx^2 f(\vx)\text{ or }\mH( f)(\vx)$ & The Hessian matrix of $f$ at input point $\vx$\\
-$\displaystyle \int f(\vx) d\vx $ & Definite integral over the entire domain of $\vx$ \\
-$\displaystyle \int_\sS f(\vx) d\vx$ & Definite integral with respect to $\vx$ over the set $\sS$ \\
-\end{tabular}
-\egroup
-\vspace{0.25cm}
-
-\centerline{\bf Probability and Information Theory}
-\bgroup
-\def\arraystretch{1.5}
-\begin{tabular}{p{1.25in}p{3.25in}}
-$\displaystyle P(\ra)$ & A probability distribution over a discrete variable\\
-$\displaystyle p(\ra)$ & A probability distribution over a continuous variable, or over
-a variable whose type has not been specified\\
-$\displaystyle \ra \sim P$ & Random variable $\ra$ has distribution $P$\\% so thing on left of \sim should always be a random variable, with name beginning with \r
-$\displaystyle  \E_{\rx\sim P} [ f(x) ]\text{ or } \E f(x)$ & Expectation of $f(x)$ with respect to $P(\rx)$ \\
-$\displaystyle \Var(f(x)) $ &  Variance of $f(x)$ under $P(\rx)$ \\
-$\displaystyle \Cov(f(x),g(x)) $ & Covariance of $f(x)$ and $g(x)$ under $P(\rx)$\\
-$\displaystyle H(\rx) $ & Shannon entropy of the random variable $\rx$\\
-$\displaystyle \KL ( P \Vert Q ) $ & Kullback-Leibler divergence of P and Q \\
-$\displaystyle \mathcal{N} ( \vx ; \vmu , \mSigma)$ & Gaussian distribution %
-over $\vx$ with mean $\vmu$ and covariance $\mSigma$ \\
-\end{tabular}
-\egroup
-\vspace{0.25cm}
-
-\centerline{\bf Functions}
-\bgroup
-\def\arraystretch{1.5}
-\begin{tabular}{p{1.25in}p{3.25in}}
-$\displaystyle f: \sA \rightarrow \sB$ & The function $f$ with domain $\sA$ and range $\sB$\\
-$\displaystyle f \circ g $ & Composition of the functions $f$ and $g$ \\
-  $\displaystyle f(\vx ; \vtheta) $ & A function of $\vx$ parametrized by $\vtheta$.
-  (Sometimes we write $f(\vx)$ and omit the argument $\vtheta$ to lighten notation) \\
-$\displaystyle \log x$ & Natural logarithm of $x$ \\
-$\displaystyle \sigma(x)$ & Logistic sigmoid, $\displaystyle \frac{1} {1 + \exp(-x)}$ \\
-$\displaystyle \zeta(x)$ & Softplus, $\log(1 + \exp(x))$ \\
-$\displaystyle || \vx ||_p $ & $\normlp$ norm of $\vx$ \\
-$\displaystyle || \vx || $ & $\normltwo$ norm of $\vx$ \\
-$\displaystyle x^+$ & Positive part of $x$, i.e., $\max(0,x)$\\
-$\displaystyle \1_\mathrm{condition}$ & is 1 if the condition is true, 0 otherwise\\
-\end{tabular}
-\egroup
-\vspace{0.25cm}
-
-\section{Final instructions}
-Do not change any aspects of the formatting parameters in the style files.
-In particular, do not modify the width or length of the rectangle the text
-should fit into, and do not change font sizes (except perhaps in the
-\textsc{References} section; see below). Please note that pages should be
-numbered.
-
-\section{Preparing PostScript or PDF files}
-
-Please prepare PostScript or PDF files with paper size ``US Letter'', and
-not, for example, ``A4''. The -t
-letter option on dvips will produce US Letter files.
-
-Consider directly generating PDF files using \verb+pdflatex+
-(especially if you are a MiKTeX user).
-PDF figures must be substituted for EPS figures, however.
-
-Otherwise, please generate your PostScript and PDF files with the following commands:
-\begin{verbatim}
-dvips mypaper.dvi -t letter -Ppdf -G0 -o mypaper.ps
-ps2pdf mypaper.ps mypaper.pdf
-\end{verbatim}
-
-\subsection{Margins in LaTeX}
-
-Most of the margin problems come from figures positioned by hand using
-\verb+\special+ or other commands. We suggest using the command
-\verb+\includegraphics+
-from the graphicx package. Always specify the figure width as a multiple of
-the line width as in the example below using .eps graphics
-\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.eps}
-\end{verbatim}
-or % Apr 2009 addition
-\begin{verbatim}
-   \usepackage[pdftex]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.pdf}
-\end{verbatim}
-for .pdf graphics.
-See section~4.4 in the graphics bundle documentation (\url{http://www.ctan.org/tex-archive/macros/latex/required/graphics/grfguide.ps})
-
-A number of width problems arise when LaTeX cannot properly hyphenate a
-line. Please give LaTeX hyphenation hints using the \verb+\-+ command.
+\section{Introduction}
 
@@
 
-\bibliography{iclr2020_conference}
+\bibliography{bibliography}
 \bibliographystyle{iclr2020_conference}

### 2019-09-10 reports/iclr/paper.tex
Add current state of notes

@@
 \usepackage{url}
+
+% ADDED BY US
+\usepackage{booktabs}
+\usepackage{graphicx}
+\usepackage{xcolor}
+\usepackage{cleveref}
+
+\definecolor{red}{HTML}{e74c3c}
+\definecolor{blue}{HTML}{3498db}
+\definecolor{green}{HTML}{2ecc71}
+% END ADDED BY US
 
@@
 
-\section{Introduction}
+\section{Attention Layer Can Implement CNN}
+
+Our goal is to show that attention layers have the expressive power to learn 
+convolution filter and that we can learn such filters in practice.
+%
+The ability of the Attention mechanism to encode spacial filters (3$\times$3 kernels) 
+depends heavily on how we encode position in the image.
+
+Understanding how attention can apply convolutions can help to:
+\begin{itemize}
+  \item find better position encoding scheme,
+  \item explain the need of multiple heads.
+\end{itemize}
+
+We take inspiration from \citep[TransformerXL]{dai2019transformerxl} to define relative positional encoding.
+They decompose the computation of the attention coefficients as follow:
+\begin{align}
+    \mathbf{A}_{i, j}^{\mathrm{abs}} &= (\mE_{x_i} + \mU_i)^\top \mW_q^\top \mW_k (\mE_{x_j} + \mU_j)\\
+  %
+  %
+ &=
+  \underbrace{\mathbf{E}_{x_{i}}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k} \mathbf{E}_{x_{j}}}_{(a)} 
+  +
+  \underbrace{\mathbf{E}_{x_{i}}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k} \mathbf{U}_{j}}_{(b)}
+  +
+  \underbrace{\mathbf{U}_{i}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k} \mathbf{E}_{x_{j}}}_{(c)}
+  +
+  \underbrace{\mathbf{U}_{i}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k} \mathbf{U}_{j}}_{(d)}
+\end{align}
+with $\mE_{x_i}$ the embedding of token $x_i$, $\mU_i$ the absolute position encoding, $\mR_{i-j}$ relative position encoding. They replace all absolute position encoding with relative ones:
+\begin{align}
+  \mathbf{A}_{i, j}^{\mathrm{rel}} &=
+  \underbrace{\mathbf{E}_{x_{i}}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k, E} \mathbf{E}_{x_{j}}}_{(a)}
+  +
+  \underbrace{\mathbf{E}_{x_{i}}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k, R} {\color{blue} \mathbf{R}_{i-j}}}_{(b)}
+  +
+  % \underbrace{{\color{red} \vu^{\top}} \mathbf{W}_{k, E} \mathbf{E}_{x_{j}}}_{(c)}
+  +
+  \underbrace{{\color{red} \vv^{\top}} \mathbf{W}_{k, R} {\color{blue} \mathbf{R}_{i-j}}}_{(d)}
+  \label{eq:att_rel}
+\end{align}
+
+To mimic the CNN computation, each attention head focuses on a pixel at a given relative position.
+Hence reproducing a $3\times 3$ kernel requires 9 attention heads and the ability for each of them to perfectly attend on
+one pixel at a relative position.
+Given that spatial convolution filters are not conditioned on the input data, we set $\mW_{k, E}$ and $\mW_{k, R}$ to 0, leaving only the (d) term in \eqref{eq:att_rel}.
+We further write the attention computation in the 2D setting,
+\begin{align}
+  \mathbf{A}_{i, j}^{\mathrm{conv}} &= \vv^{\top} \mathbf{W}_{k, R} {\color{blue} \mathbf{R}_{\vp_i - \vp_j}}
+\end{align}
+with $\vp_i$ the row and column position of pixel $i$.
+As both $\vv$ and $\mathbf{W}_{k, R}$ are learnable parameters, we simplify the expression to learn a single vector $\mathbf{t}_h$ for each head $h$.
+
+\subsection{Attention on a Pixel at any Relative Position}
+
+\paragraph{How to discern relative position?} The goal is to reproduce the $3\times 3$ pattern of CNN kernel with attention instead.
+Each head should be able to chose which pixel to attend based on its relative position to the query token $x_i$.
+The most basic attention mechanism is the dot product $(\vp_i - \vp_j)^\top \mathbf{t}_h$ between the relative positions of the input pixels and the relative target positions $\mathbf{t}_h = (x_h, y_h)^\top$.
+The dot product is large for pixels in the same direction as $\mathbf{t}_h$, however it also grows for farther pixels.
+To be able to focus on a relative pixel position (direction and distance), we propose the following relative position encoding
+\begin{align}
+  \mR_{\Delta} = 
+  \begin{pmatrix} 
+  \Delta_x& \Delta_y& \Delta_x^2& \Delta_y^2& 1& 1
+  \end{pmatrix}^\top
+\end{align}
+Instead of learning the target vector $\mathbf{t}_h$, we parametrize it for each head to attend to the relative pixel position~$(x_h, y_h)$,
+\begin{align}
+  \mathbf{t}_h= 
+  -\alpha_h \begin{pmatrix} 
+  -2 x_h& -2 y_h& 1& 1&  x_h^2&  y_h^2
+  \end{pmatrix}^\top
+\end{align}
+The attention coefficient for head $h$ between pixel $i$ and $j$ is given by the dot product,
+\begin{align}
+  \mR_{\Delta}^\top \mathbf{t}_h = -\alpha_h ( (\Delta_x - x_h)^2 + (\Delta_y - y_h) ^2 ),
+\end{align}
+with $\Delta = \vp_i - \vp_j$. 
+The maximum attention coefficient is 0 when $\Delta = (x_h, y_h)$, i.e. the center of attention of a given head.
+The $\alpha$ coefficient controls how spiky the attention is (analogous to temperature in the softmax).
+\Cref{fig:attention_cnn} gives a representation of the attention weights for a fixed query pixel $i$ and different $\alpha$ and $(x_h, y_h)$.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=1\linewidth]{plots/conv_attention.pdf}
+  \caption{Attention coefficient for different center $i$ and target $j$ with varying $\alpha$ parameters. Target designate the relative position that the head attends to.}
+  \label{fig:attention_cnn}
+\end{figure}
+
+\paragraph{Discussion.} Some relations can be drawn to RBF kernels centered at the target pixels.
+We are expressing a more general form of convolutions where
+\emph{(i)} the input pixels do not follow a grid shape but has any pattern and 
+\emph{(ii)} the inputs are not single pixels but weighted averages of local patches in the image.
+
+\paragraph{Simplification.} One further simplification is to remove the constant terms of $\mR_{\Delta}$ because the softmax (renormalization) is shift invariant and constant terms for a head are useless.
+
+\subsection{Non Isotropic Gaussian}
+
+In this section, we present an extension of the relative positional encoding introduced above
+to model non-isotropic Gaussians.
+
+\begin{align}
+  f_{\mu, \Sigma}(\vx) = \exp \left(
+    - \frac 1 2
+    (\vx - \mu)^\top \Sigma^{-1} (\vx - \mu)
+  \right)
+\end{align}
+We drop the normalization factor of the Gaussian distribution as it is replaced by the softmax of the attention mechanism.
+The matrix $\Sigma^{-1}$ must be positive semi-definite.
+We parametrize it as 
+\begin{align}
+  \Sigma^{-1} = (\Sigma^{-1/2})^\top\Sigma^{-1/2} = \begin{pmatrix}a & b \\ b & c\end{pmatrix}  
+\end{align}
+Our goal is to write the exponent as a dot product of two vectors:
+\begin{itemize}
+  \item one vector $R_\vx$ dependent only on $\vx$, the relative positional encoding,
+  \item one vector $\mathbf{t}_h$ dependent only on $\mu$ and $\Sigma$, the attention head.
+\end{itemize}
+\begin{align}
+  R_\vx &= 
+  \begin{pmatrix}
+    x_1      & x_2       & x_1      & x_2      & x_1^2   & x_2^2 & x_1 x_2 & 1        & 1         & 1
+  \end{pmatrix}\\
+  \mathbf{t}_h &= -\frac{1}{2}
+  \begin{pmatrix}
+    -2a\mu_1 & -2c \mu_2 & -2b\mu_2 & -2b\mu_1 & a       & c     & 2b      & a\mu_1^2 & c\mu_2^2 & 2b\mu_1 \mu_2
+  \end{pmatrix}\\
+  R_\vx^\top \mathbf{t}_h &=
+  -\frac{1}{2} 
+  \left[
+  a(x_1 - \mu_1)^2 + 2b(x_1-\mu_1)(x_2 -\mu_2) + c(x_2-\mu_2)^2 
+  \right]
+  = - \frac 1 2 (\vx - \mu)^\top \Sigma^{-1} (\vx - \mu)
+\end{align}
+We can check that setting $b = 0$ and $a=c=\alpha$ recovers the expression of the isotropic Gaussian derived above.
+
+\subsection{Extensions of the Attention Mechanism?} 
+\begin{itemize}
+
+  \item Does the terms (a) (b) (c) allow to condition the CNN filters on the input data?
+\end{itemize}
+
+\section{Experiments}
+
+We want to validate that not only Transformer architecture can express CNN filters
+but that it can also learn such filters with SGD from the data.
+%
+It has already been shown by \citep{belloAttentionAugmentedConvolutional2019} that 
+adding attention features to CNNs can improve performence on Cifar-100 and ImageNet.
+%
+We want to stick to a fully attentional model, and show that it matches its siblings ResNet of equivalent depth.
+
+\subsection{Performance Against ResNet}
+
+We design a smaller ResNet (i.e. ResNet10) which have similar number of layers as our transformer.
+The sizes of the models are displayed in Table~\ref{tab:parameter_size}.
+
+\begin{table}
+  \centering
+  \begin{tabular}{cc}
+    \toprule
+    Model & Number of parameters\\
+    \midrule
+    ResNet10 & 4.9M\\
+    BERT 4 layers & 1.85M\\
+    BERT 6 layers & 9.56M \\
+    \bottomrule
+  \end{tabular}
+  \caption{Number of parameters per model.}
+  \label{tab:parameter_size}
+\end{table}
+
+\begin{figure}[h!]
+\includegraphics[width=.16\linewidth]{plots/attention/layer_0.png}
+\includegraphics[width=.16\linewidth]{plots/attention/layer_1.png}
+\includegraphics[width=.16\linewidth]{plots/attention/layer_2.png}
+\includegraphics[width=.16\linewidth]{plots/attention/layer_3.png}
+\includegraphics[width=.16\linewidth]{plots/attention/layer_4.png}
+\includegraphics[width=.16\linewidth]{plots/attention/layer_5.png}
+\caption{Contours of attention weights per layer for the 6 layers fully attentional model.}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=.13\linewidth]{plots/attention_training/layer_3_0.png}
+\includegraphics[width=.13\linewidth]{plots/attention_training/layer_3_1.png}
+\includegraphics[width=.13\linewidth]{plots/attention_training/layer_3_2.png}
+\includegraphics[width=.13\linewidth]{plots/attention_training/layer_3_3.png}
+\includegraphics[width=.13\linewidth]{plots/attention_training/layer_3_4.png}
+\includegraphics[width=.13\linewidth]{plots/attention_training/layer_3_5.png}
+\includegraphics[width=.13\linewidth]{plots/attention_training/layer_3_6.png}
+\caption{Contours of attention weights during training (300 epochs) at layer 3.}
+\end{figure}
+
+\begin{figure}[h]
+  \includegraphics[width=.4\linewidth]{plots/eval_accuracy_plot.png}
+  \hfill
+  \includegraphics[width=.6\linewidth]{plots/eval_accuracy_legend.png}
+  \caption{Evaluation accuracy on CIFAR-10 of a small ResNet and two Gaussian Attention models.}
+\end{figure}
+
+\section{Convolutional Layer}
+
+A convolution layer is defined by the size of its kernel
+The output of one layer of convolution for an input $\mX \in \R^{W\times H \times C}$ is
+% \begin{align}
+%   \mX'[r,c] &= 
+% \end{align}
 

### 2019-09-10 reports/iclr/paper.tex
Update to ICLR notation
Add table compare attentions + restructure

@@
 
-\section{Attention Layer Can Implement CNN}
+\section{Introduction}
+
+\section{Background on Attention Mechanism and Related Work}
+
+\subsection{Convolution Layer}
+
+A convolution layer is defined by the size of its kernel
+The output of one layer of convolution for an input $\mX \in \R^{W\times H \times C}$ is
+% \begin{align}
+%   \mX'[r,c] &= 
+% \end{align}
+
+\subsection{Self Attention Layer}
+
+\subsection{Attention Mechanism in Vision}
+
+Successful work to use attention on images \citep{ramachandran2019standaloneselfattention,belloAttentionAugmentedConvolutional2019}.
+
+\begin{table}[h]
+  \centering
+  \begin{tabular}{lccc}
+    \toprule
+    Model&relative&sinusoids&learned\\
+    \midrule
+    \cite{vaswani17attentionisallyouneed} & & \checkmark\\
+    \cite{radford2018gpt2} & & & \checkmark\\
+    \cite{devlin2018bert} & & & \checkmark\\
+    \cite{dai2019transformerxl} & \checkmark & \checkmark \\
+    \cite{yang2019xlnet}  & \checkmark & \checkmark \\
+    \midrule
+    \cite{belloAttentionAugmentedConvolutional2019} & \checkmark & & \checkmark \\
+    \cite{ramachandran2019standaloneselfattention} & \checkmark & & \checkmark \\
+    % Images
+    \bottomrule
+  \end{tabular}
+  \caption{Type of position encoding used by transformers models applied to text (\emph{top}) and images (\emph{bottom}). 
+  When multiple types have been tried by the authors, we report the one advised.}
+  \label{tab:relwork_attention}
+\end{table}
+
+\section{Attention Layer Can Implement Convolution Layer}
 
@@
   +
-  % \underbrace{{\color{red} \vu^{\top}} \mathbf{W}_{k, E} \mathbf{E}_{x_{j}}}_{(c)}
+  \underbrace{{\color{red} \vu^{\top}} \mathbf{W}_{k, E} \mathbf{E}_{x_{j}}}_{(c)}
   +
@@
 \begin{align}
-  f_{\mu, \Sigma}(\vx) = \exp \left(
+  f_{\vmu, \mSigma}(\vx) = \exp \left(
     - \frac 1 2
-    (\vx - \mu)^\top \Sigma^{-1} (\vx - \mu)
+    (\vx - \vmu)^\top \mSigma^{-1} (\vx - \vmu)
   \right)
@@
 We drop the normalization factor of the Gaussian distribution as it is replaced by the softmax of the attention mechanism.
-The matrix $\Sigma^{-1}$ must be positive semi-definite.
+The matrix $\mSigma^{-1}$ must be positive semi-definite.
 We parametrize it as 
 \begin{align}
-  \Sigma^{-1} = (\Sigma^{-1/2})^\top\Sigma^{-1/2} = \begin{pmatrix}a & b \\ b & c\end{pmatrix}  
+  \mSigma^{-1} = (\mSigma^{-1/2})^\top\mSigma^{-1/2} = \begin{pmatrix}a & b \\ b & c\end{pmatrix}  
 \end{align}
@@
   \item one vector $R_\vx$ dependent only on $\vx$, the relative positional encoding,
-  \item one vector $\mathbf{t}_h$ dependent only on $\mu$ and $\Sigma$, the attention head.
+  \item one vector $\mathbf{t}_h$ dependent only on $\vmu$ and $\mSigma$, the attention head.
 \end{itemize}
@@
   \right]
-  = - \frac 1 2 (\vx - \mu)^\top \Sigma^{-1} (\vx - \mu)
+  = - \frac 1 2 (\vx - \vmu)^\top \mSigma^{-1} (\vx - \vmu)
 \end{align}
@@
 
-\subsection{Extensions of the Attention Mechanism?} 
+\subsection{Implications to Sinusoid or Learned Positional Encoding}
+
+\subsection{Exploit Attention on Features?} 
 \begin{itemize}
@@
 
-\begin{figure}[h!]
+\begin{figure}[h]
 \includegraphics[width=.16\linewidth]{plots/attention/layer_0.png}
@@
 
-\begin{figure}[h!]
+\begin{figure}[h]
 \includegraphics[width=.13\linewidth]{plots/attention_training/layer_3_0.png}
@@
 
-\section{Convolutional Layer}
+\section{Discussion}
 
-A convolution layer is defined by the size of its kernel
-The output of one layer of convolution for an input $\mX \in \R^{W\times H \times C}$ is
-% \begin{align}
-%   \mX'[r,c] &= 
-% \end{align}
-
-\subsubsection*{Author Contributions}
-If you'd like to, you may include  a section for author contributions as is done
-in many journals. This is optional and at the discretion of the authors.
+% \subsubsection*{Author Contributions}
+% If you'd like to, you may include  a section for author contributions as is done
+% in many journals. This is optional and at the discretion of the authors.
 
@@
 
-\appendix
-\section{Appendix}
-You may include other additional sections here.
+% \appendix
+% \section{Appendix}
+% You may include other additional sections here.
 

### 2019-09-10 reports/iclr/paper.tex
Add CNN and Attention equations

@@
 \usepackage{cleveref}
+
+\usepackage{todonotes}
+\setlength{\marginparwidth}{3.4cm}
 
@@
 
+Attention mechanism were introduced in Neural Machine Translation to better handle long range dependencies and align pairs of sentences \citep{Bahdanau2015attention}.
+
 \section{Background on Attention Mechanism and Related Work}
+
+We briefly recall the formulation of standard CNN layers and Self-Attention layers using unified notation.
 
@@
 
-A convolution layer is defined by the size of its kernel
-The output of one layer of convolution for an input $\mX \in \R^{W\times H \times C}$ is
-% \begin{align}
-%   \mX'[r,c] &= 
-% \end{align}
+A convolution layer is defined by its kernel size $K$ (assuming square kernel for simplicity), the number of input channel $C_{in}$ and the number of output channel $C_{out}$. 
+It is parametrized by a kernel tensor $\tW~\in~\R^{K\times K \times C_{out} \times C_{in}}$ and a bias vector $\vb~\in~\R^{C_{out}}$.
+Given an input image $\tX~\in~\R^{W\times H \times C}$ of width $W$, height $H$ and $C$ channels, 
+the output of the convolution layer is given by,
+%
+\begin{align}
+  \tY_{i,j,:} = 
+  \vb 
+  +
+  \sum_{(m, n) \in \{\lfloor (K-1) / 2 \rfloor, \dots, \lfloor K / 2 \rfloor\}^2}
+  \mW_{m,n,:,:}
+  \tX_{i+m, j+n, :}
+\end{align}
+%
 
-\subsection{Self Attention Layer}
+\subsection{Self-Attention Layer}
+
+A Self-Attention layer is defined by its hidden dimension $d_{h}$ and its number of heads $K$.
+\todo{JB: same as size of the CNN kernel, we point that they are related ($K^2$) but need clarify notation} %
+It is parametrized by
+$\tW^Q \in \R^{K \times d \times d_{h}}$ query layer, $\tW^V \in \R^{K \times d \times d_{h}}$ key layer, $\tW^V \in \R^{K \times d \times d_{h}}$ value layer, a projection layer $\tW^Q \in \R^{K \times d_{h} \times d}$ and output layer $\mW^O \in \R^{(Kd_{h})\times d}$.
+%
+Applied to an input $\mX \in \R^{T\times d}$, the output of the Self-Attention layer is computed as,
+%
+\begin{align}
+  \mA_k &= \operatorname{softmax}
+  \left(
+    (\mX \mW_k^K)(\mX \mW_k^Q)^\top
+  \right)\,, \\
+  %
+  \mH_{t,:} &= 
+  \sum_{k \in {1,\dots, K}} 
+  \mA_k
+  \mX
+  \mW_k^P
+  \,,\\
+  %
+  \mY_{t,:} &= \mH_{t,:} \mW^O + \mX_{t,:}\,,
+\end{align}
+where the $\operatorname{softmax}(\cdot)$ is taken over all the dimensions of the tensor but the first one. For simplicity, we exclude the batch normalization layers.%
+\todo{JB: check dimensions and readability}%
 
@@
   \end{tabular}
-  \caption{Type of position encoding used by transformers models applied to text (\emph{top}) and images (\emph{bottom}). 
-  When multiple types have been tried by the authors, we report the one advised.}
+  \caption{Types of position encoding used by transformers models applied to text (\emph{top}) and images (\emph{bottom}). 
+  When multiple encoding types have been tried, we report the one advised by the authors.}
   \label{tab:relwork_attention}

### 2019-09-11 train.py
Update train checkpointing

@@ -79,8 +79,8 @@ config = OrderedDict(
     # === LOGGING ===
     only_time_one_epoch=False,  # show timer after 1 epoch and stop
     only_list_parameters=False,
+    num_keep_checkpoints=10,
     plot_attention_positions=True,
-    experiment_name=None,
     output_dir="./output.tmp",
 )
 # fmt: on
@@ -100,35 +100,22 @@ def main():
     Directory structure:
 
       output_dir
-      |-- experiment_name
-            |-- config.yaml
-            |-- best.checkpoint
-            |-- last.checkpoint
-      |-- 00_logdir
-            |-- experiment_name
-                |-- tensorboard logs...
-
-    If no `experiment_name` is given, save output directly in `output_dir`
-    and does not log for tensorboard.
-    Point tensorboard to `00_logdir`.
+        |-- config.yaml
+        |-- best.checkpoint
+        |-- last.checkpoint
+        |-- tensorboard logs...
     """
 
     global output_dir
-    output_dir = os.path.join(config["output_dir"], config["experiment_name"] or "")
-    os.makedirs(output_dir, exist_ok=True)
-    logdir = None
-    if config["experiment_name"]:
-        logdir = os.path.join(config["output_dir"], "00_logdir", config["experiment_name"])
+    output_dir = config["output_dir"]
+    os.makedirs(output_dir, exist_ok = True)
 
     # save config in YAML file
     store_config()
 
     # create tensorboard writter
-    if logdir:
-        writer = SummaryWriter(logdir=logdir, max_queue=100, flush_secs=10)
-        print(f"Tensorboard logs saved in '{logdir}'")
-    else:
-        writer = DummySummaryWriter()
+    writer = SummaryWriter(logdir=output_dir, max_queue=100, flush_secs=10)
+    print(f"Tensorboard logs saved in '{output_dir}'")
 
     # Set the seed
     torch.manual_seed(config["seed"])
@@ -151,6 +138,9 @@ def main():
 
     # We keep track of the best accuracy so far to store checkpoints
     best_accuracy_so_far = utils.accumulators.Max()
+    checkpoint_every_n_epoch = None
+    if config["num_keep_checkpoints"] > 0:
+        checkpoint_every_n_epoch = max(1, config["num_epochs"] // config["num_keep_checkpoints"])
     global_step = 0
 
     for epoch in range(config["num_epochs"]):
@@ -288,6 +278,8 @@ def main():
[…]

### 2019-09-11 train.py
Clean up and remove Mask

@@ -68,11 +68,6 @@ config = OrderedDict(
     attention_type="gaussian",                           # type of attention : "dilation" or "gaussian"
     attention_isotropic_gaussian=False,
     attention_gaussian_blur_trick=False,                 # use a computational trick for gaussian attention to avoid computing the attention probas
-    attention_dilation=2,
-    attention_local_patch_size=5,
-    loss_mask_dimension=5,
-    loss_inpainting_weight=0.5,
-    loss_classification_only=True,
     pooling_concatenate_size=2,                          # concatenate the pixels value by patch of pooling_concatenate_size x pooling_concatenate_size to redude dimension
     pooling_use_resnet=False,
 
@@ -174,7 +169,7 @@ def main():
         time_i = 0
         loader_time_context = timer("loader")
         loader_time_context.__enter__()
-        for batch_x, batch_y, batch_mask in tqdm(training_loader):
+        for batch_x, batch_y in tqdm(training_loader):
 
             loader_time_context.__exit__(None, None, None)
             with timer("move_to_device"):
@@ -200,21 +195,6 @@ def main():
                 classification_loss = criterion(prediction, batch_y)
                 loss = classification_loss
 
-                # TODO check mask is 1 for keep and 0 for hide
-                # mask_selector = ~reconstruction_mask.unsqueeze(1)
-                # masked_input = torch.masked_select(reconstruction, mask_selector)
-                # masked_output = torch.masked_select(image_out, mask_selector)
-
-                # inpainting_loss = ((masked_input - masked_output) ** 2).mean()
-
-                # # TODO weighting of the two losses
-                # if config["loss_classification_only"]:
-                #     loss = classification_loss
-                # else:
-                #     loss = classification_loss * (1 - config["loss_inpainting_weight"]) + (
-                #         inpainting_loss * config["loss_inpainting_weight"]
-                #     )
-
             acc = accuracy(prediction, batch_y)
 
             with timer("backward"):
@@ -224,12 +204,6 @@ def main():
             with timer("weights_update"):
                 optimizer.step()
 
-            # writer.add_scalar(
-            #     "train/classification_loss", classification_loss / config["batch_size"], global_step
-            # )
-            # writer.add_scalar(
-            #     "train/inpainting_loss", inpainting_loss / config["batch_size"], global_step
-            # )
             writer.add_scalar("train/loss", loss, global_step)
[…]

### 2019-09-11 reports/iclr/paper.tex
Start writing intro

@@
 \usepackage{cleveref}
+\usepackage{multirow}
 
@@
 paragraph.
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 \end{abstract}
@@
 
-Attention mechanism were introduced in Neural Machine Translation to better handle long range dependencies and align pairs of sentences \citep{Bahdanau2015attention}.
+Recent advances in Natural Language Processing (NLP) are due to pretraining of large models based on the Transformers architecture~\citep{vaswani17attentionisallyouneed}. 
+%
+%
+How Transformers process input text differs significantly from Recurrent Neural Networks as it does not ingest the text from left to right (or right to left) but each token representation can leverage all other tokens of the sentence.
+% 
+The core of Transformers resides in the Self-Attention mechanism.
+%
+The attention mechanism was originally introduced in Neural Machine Translation to better handle long range dependencies and align pairs of sentences to translate~\citep{Bahdanau2015attention}.
+
+The success of such architectures in NLP made us reconsider the absolute dominance of the Convolutional Layers in vision and question its supremacy.
+%
+Applying the transformer architecture to images is only stepping up one dimension but involves some technical challenges of scale.
+%
+In \Cref{sec:background} we review these challenges and present advances using Transformers on images.
+
+\todo{JB: Need to introduce multi-head before}
+We show in \Cref{sec:background} that this success is not so surprising. 
+%
+In fact, Self-Attention layers have the expressive power to encode CNN layers under very basic conditions: (i) positional encoding must be relative to the position of the computed value, (ii) self-attention requires multiple heads (iii) positional encoding can be fixed to pixel position difference with second order combinations.
+%
+\todo{JB: I don't show that (iii) is necessary but it's an example, not sure how to state that it does not require a crazy encoding schema.}
+%
+We show that Self-Attention layers generalize CNN layers to not only learn the filters but also the position of the ``attended'' pixels.
+
+The ability for Self-Attention layer to express CNN does not ensure that such filters are learnable.
+%
+Through experiments, we demonstrate that standalone self-attention models can perform as well as well established ResNet.
+%
+Our experimental part (\cref{sec:experiments}) focuses more on the interpretation of this expressive power and investigate different type of positional encoding.
+%
+It is particularly interesting to study such positional encoding schema on images, where we have a good intuition, to then transfer the lessons learned to NLP, where distances between words and absolute positions in the sentence can vary greatly between languages and seem less concrete.
+%
 
 \section{Background on Attention Mechanism and Related Work}
+\label{sec:background}
 
-We briefly recall the formulation of standard CNN layers and Self-Attention layers using unified notation.
+We first recall the formulation of standard CNN layers and Self-Attention layers using unified notation.
+We then review how recent lines of work have incorporated Self-Attention layers into classical ResNet architecture for vision \citep{ramachandran2019standaloneselfattention,belloAttentionAugmentedConvolutional2019}.
 
@@
 
-A convolution layer is defined by its kernel size $K$ (assuming square kernel for simplicity), the number of input channel $C_{in}$ and the number of output channel $C_{out}$. 
+A convolution layer is defined by a kernel size $K$ (assuming square kernel for simplicity), a number of input channel $C_{in}$ and a number of output channel $C_{out}$. 
 It is parametrized by a kernel tensor $\tW~\in~\R^{K\times K \times C_{out} \times C_{in}}$ and a bias vector $\vb~\in~\R^{C_{out}}$.
@@
 \end{align}
-where the $\operatorname{softmax}(\cdot)$ is taken over all the dimensions of the tensor but the first one. For simplicity, we exclude the batch normalization layers.%
+where the $\operatorname{softmax}(\cdot)$ is taken over all the dimensions of the tensor but the first one. For simplicity, we exclude the batch normalization layers and constant factors.%
 \todo{JB: check dimensions and readability}%
@@
 
-Successful work to use attention on images \citep{ramachandran2019standaloneselfattention,belloAttentionAugmentedConvolutional2019}.
+A recent trend emerged using Self-Attention to solve vision tasks.
+%
+It is mainly motivated by the ability of attention mechanism to model long range dependencies across different part of images and help solving Visual Question Answering tasks. \todo{JB: cite}
+% 
+Successful works have reached the level of accuracy of ResNets on classification tasks for Cifar and ImageNet datasets. 
+%
+Along with these impressive results, \cite{belloAttentionAugmentedConvolutional2019} advocate for using Self-Attention layers along with classical convolutions to reach best performance.
+%
+\cite{ramachandran2019standaloneselfattention} show that even standalone Self-Attention can be enough and propose strategies to downsample the image to reduce the number of pixel-to-pixel attention score to compute and store in memory.
+
+There are two main challenges in reusing Self-Attention, originally designed for text, for images:
+\paragraph{Positional Encoding.}
+%
+\paragraph{Downsampling.}
 
@@
   \centering
-  \begin{tabular}{lccc}
+  \begin{tabular}{lcccc}
     \toprule
-    Model&relative&sinusoids&learned\\
+    \multirow{2}{*}{Model}&\multicolumn{3}{c}{type of positional encoding}&\multirow{2}{*}{relative}\\
+    \cmidrule(r){2-4}
+    &sinusoids&learned&quadratic\\
     \midrule
-    \cite{vaswani17attentionisallyouneed} & & \checkmark\\
-    \cite{radford2018gpt2} & & & \checkmark\\
-    \cite{devlin2018bert} & & & \checkmark\\
-    \cite{dai2019transformerxl} & \checkmark & \checkmark \\
-    \cite{yang2019xlnet}  & \checkmark & \checkmark \\
+    \cite{vaswani17attentionisallyouneed} & \checkmark\\
+    \cite{radford2018gpt2} & & \checkmark\\
+    \cite{devlin2018bert} & & \checkmark\\
+    \cite{dai2019transformerxl} & \checkmark & & & \checkmark \\
+    \cite{yang2019xlnet}  & \checkmark & & & \checkmark \\
     \midrule
-    \cite{belloAttentionAugmentedConvolutional2019} & \checkmark & & \checkmark \\
-    \cite{ramachandran2019standaloneselfattention} & \checkmark & & \checkmark \\
-    % Images
+    \cite{belloAttentionAugmentedConvolutional2019} & & \checkmark && \checkmark \\
+    \cite{ramachandran2019standaloneselfattention} & & \checkmark && \checkmark \\
+    Our work & & & \checkmark & \checkmark \\
     \bottomrule
   \end{tabular}
-  \caption{Types of position encoding used by transformers models applied to text (\emph{top}) and images (\emph{bottom}). 
+  \caption{Types of positional encoding used by transformers models applied to text (\emph{top}) and images (\emph{bottom}). 
   When multiple encoding types have been tried, we report the one advised by the authors.}
@@
 
-\section{Attention Layer Can Implement Convolution Layer}
+\section{Self-Attention Layer Can Implement Convolution Layer}
+\label{sec:attention_can_implement_cnn}
 
@@
 
-\subsection{Implications to Sinusoid or Learned Positional Encoding}
+\subsection{Implications to Sinusoid and Learned Positional Encoding}
 
@@
 \section{Experiments}
+\label{sec:experiments}
 
@@
 \section{Discussion}
+\label{sec:discussion}
 

### 2019-09-11 reports/iclr/paper.tex
Update paper

@@
 %
-Applying the transformer architecture to images is only stepping up one dimension but involves some technical challenges of scale.
+Applying the transformer architecture from text to images is only stepping up one dimension but involves some technical challenges of scale.
 %
-In \Cref{sec:background} we review these challenges and present advances using Transformers on images.
+In \cref{sec:background} we review these challenges and present advances using Transformers on images.
 
 \todo{JB: Need to introduce multi-head before}
-We show in \Cref{sec:background} that this success is not so surprising. 
+We show in \cref{sec:attention_can_implement_cnn} that this success is not so surprising. 
 %
@@
 %
-Our experimental part (\cref{sec:experiments}) focuses more on the interpretation of this expressive power and investigate different type of positional encoding.
+Our experiments (in \cref{sec:experiments}) focus more on the interpretation of this expressive power and investigate different type of positional encoding.
 %
@@
 \begin{align}
-  \mA_k &= \operatorname{softmax}
-  \left(
-    (\mX \mW_k^K)(\mX \mW_k^Q)^\top
-  \right)\,, \\
+  \mA_k &= 
+    (\mX \mW_k^Q)(\mX \mW_k^K)^\top
+  \,, \label{eq:att_coeff}\\
   %
   \mH_{t,:} &= 
-  \sum_{k \in {1,\dots, K}} 
+  \sum_{k \in \{1,\dots, K\}} 
+  \operatorname{softmax}
+  \left(
     \mA_k
+  \right)
   \mX
+  \mW_k^V
   \mW_k^P
@@
   \mY_{t,:} &= \mH_{t,:} \mW^O + \mX_{t,:}\,,
+  \label{eq:attention}
 \end{align}
@@
 
+% explain the plan to show expressivity
 Our goal is to show that attention layers have the expressive power to learn 
@@
 
-Understanding how attention can apply convolutions can help to:
-\begin{itemize}
-  \item find better position encoding scheme,
-  \item explain the need of multiple heads.
-\end{itemize}
+\subsection{Relative Position Encoding and Translation Equivariance}
+\label{ssec:relative_position_encoding}
 
-We take inspiration from \citep[TransformerXL]{dai2019transformerxl} to define relative positional encoding.
-They decompose the computation of the attention coefficients as follow:
+Note that the Self-Attention mechanism (\ref{eq:attention}) is equivarient to reordering.
+%
+It means that shuffling the order of the tokens does not affect the meaning extracted by the model.
+%
+To alleviate this problem, an embedding is learned for each position in a sentence (or pixel in an image) and added to the representation of the token before applying self-attention.
 \begin{align}
-    \mathbf{A}_{i, j}^{\mathrm{abs}} &= (\mE_{x_i} + \mU_i)^\top \mW_q^\top \mW_k (\mE_{x_j} + \mU_j)\\
+  \mX_{t,:} = \mE_{x_t} + \mP_t\,,
+\end{align}
+where $\mE_{x_t}$ is the learned vector representation of the $x_t$ token and $\mP$ is a position embedding matrix defined up to a maximum length, but it could be any function that returns a vector representation of the position.
+
+Relative position encoding was introduced by \cite{dai2019transformerxl} in TransformerXL. 
+%
+The main idea is to use the position difference between the query token (token we compute the representation of) and the key token (token we attend) instead of only the absolute position of the key token.
+%
+The computation of the attention coefficients (\cref{eq:att_coeff}) can be decomposed as follows:
+%
+\begin{align}
+    \mathbf{A}_{i, j}^{\mathrm{abs}} 
+    &= (\mE_{x_i} + \mP_i) \mW^Q (\mW^K)^\top (\mE_{x_j} + \mP_j)^\top\\
   %
@@
  &=
-  \underbrace{\mathbf{E}_{x_{i}}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k} \mathbf{E}_{x_{j}}}_{(a)} 
+  \underbrace{\mE_{x_{i}} \mW^{Q} (\mW^K)^\top \mE_{x_{j}}^\top}_{(a)} 
   +
-  \underbrace{\mathbf{E}_{x_{i}}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k} \mathbf{U}_{j}}_{(b)}
+  \underbrace{\mE_{x_{i}} \mW^{Q} (\mW^{K})^\top \mP_{j}^\top}_{(b)}
   +
-  \underbrace{\mathbf{U}_{i}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k} \mathbf{E}_{x_{j}}}_{(c)}
+  \underbrace{\mP_{i}\mW^{Q} (\mW^{K})^\top \mE_{x_{j}}}_{(c)}
   +
-  \underbrace{\mathbf{U}_{i}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k} \mathbf{U}_{j}}_{(d)}
+  \underbrace{\mP_{i} \mW^{Q} (\mW^{K})^\top \mP_{j}}_{(d)}\,.
 \end{align}
-with $\mE_{x_i}$ the embedding of token $x_i$, $\mU_i$ the absolute position encoding, $\mR_{i-j}$ relative position encoding. They replace all absolute position encoding with relative ones:
+\todo{JB: maybe better notation $\mK$ for $\mW^K$}
+To simplify the notation, we considered only one attention head and dropped the subscript $k$. They replace all absolute position encoding with relative ones:
 \begin{align}
   \mathbf{A}_{i, j}^{\mathrm{rel}} &=
-  \underbrace{\mathbf{E}_{x_{i}}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k, E} \mathbf{E}_{x_{j}}}_{(a)}
+  \underbrace{\mE_{x_{i}}^{\top} \mW_{q}^{\top} \mW_{k, E} \mE_{x_{j}}}_{(a)}
   +
-  \underbrace{\mathbf{E}_{x_{i}}^{\top} \mathbf{W}_{q}^{\top} \mathbf{W}_{k, R} {\color{blue} \mathbf{R}_{i-j}}}_{(b)}
+  \underbrace{\mE_{x_{i}}^{\top} \mW_{q}^{\top} \mW_{k, R} {\color{blue} \mathbf{R}_{i-j}}}_{(b)}
   +
-  \underbrace{{\color{red} \vu^{\top}} \mathbf{W}_{k, E} \mathbf{E}_{x_{j}}}_{(c)}
+  \underbrace{{\color{red} \vu^{\top}} \mW_{k, E} \mE_{x_{j}}}_{(c)}
   +
-  \underbrace{{\color{red} \vv^{\top}} \mathbf{W}_{k, R} {\color{blue} \mathbf{R}_{i-j}}}_{(d)}
+  \underbrace{{\color{red} \vv^{\top}} \mW_{k, R} {\color{blue} \mathbf{R}_{i-j}}}_{(d)}
   \label{eq:att_rel}
 \end{align}
+
+Simply show the translation equivariance with relative encoding.
+
+\subsection{Attention on a Pixel at any Relative Position}
+
+\begin{align}
+  \tH_{i,j,:} = \sum_{k\in\{1,\dots,K\}} \delta \tX \mW^V_k
+\end{align}
+define dirac $\delta_{i,j}$ is a matrix whose elements are zero everywe
 
@@
 Given that spatial convolution filters are not conditioned on the input data, we set $\mW_{k, E}$ and $\mW_{k, R}$ to 0, leaving only the (d) term in \eqref{eq:att_rel}.
-We further write the attention computation in the 2D setting,
+%
 \begin{align}
-  \mathbf{A}_{i, j}^{\mathrm{conv}} &= \vv^{\top} \mathbf{W}_{k, R} {\color{blue} \mathbf{R}_{\vp_i - \vp_j}}
+  \mathbf{A}_{i, j}^{\mathrm{conv}} &= \vv^{\top} \mW_{k, R} {\color{blue} \mathbf{R}_{i - j}}
 \end{align}
-with $\vp_i$ the row and column position of pixel $i$.
-As both $\vv$ and $\mathbf{W}_{k, R}$ are learnable parameters, we simplify the expression to learn a single vector $\mathbf{t}_h$ for each head $h$.
-
-\subsection{Attention on a Pixel at any Relative Position}
+As both $\vv$ and $\mW_{k, R}$ are learnable parameters, we simplify the expression to learn a single vector $\mathbf{t}_h$ for each head $h$.
 

### 2019-09-12 train.py
Add use local dataset

@@ -17,6 +17,7 @@ from tensorboardX import SummaryWriter
 from collections import OrderedDict
 from termcolor import colored
 from utils.logging import get_num_parameter, human_format, DummySummaryWriter, sizeof_fmt
+from torch.utils.data import TensorDataset
 from utils.plotting import plot_attention_positions_all_layers
 from utils.config import parse_cli_overides
 import yaml
@@ -296,6 +297,23 @@ def get_dataset(test_batch_size=100, shuffle_train=True, num_workers=2, data_roo
         dataset = torchvision.datasets.CIFAR10
     elif config["dataset"] == "Cifar100":
         dataset = torchvision.datasets.CIFAR100
+    elif config["dataset"].startswith("/"):
+        train_data = torch.load(config["dataset"] + ".train")
+        test_data = torch.load(config["dataset"] + ".test")
+        training_set = TensorDataset(train_data["data"], train_data["target"])
+        test_set = TensorDataset(test_data["data"], test_data["target"])
+
+        training_loader = torch.utils.data.DataLoader(
+            training_set,
+            batch_size=config["batch_size"],
+            shuffle=shuffle_train,
+            num_workers=num_workers,
+        )
+        test_loader = torch.utils.data.DataLoader(
+            test_set, batch_size=test_batch_size, shuffle=False, num_workers=num_workers
+        )
+
+        return training_loader, test_loader
     else:
         raise ValueError("Unexpected value for config[dataset] {}".format(config["dataset"]))
 
@@ -372,7 +390,11 @@ def get_model(device):
     :param device: instance of torch.device
     :return: An instance of torch.nn.Module
     """
-    num_classes = 100 if config["dataset"] == "Cifar100" else 10
+    num_classes = 2
+    if config["dataset"] == "Cifar100":
+        num_classes = 100
+    elif config["dataset"] == "Cifar10":
+        num_classes = 10
 
     model = {
         "vgg11": lambda: models.VGG("VGG11", num_classes, batch_norm=False),

### 2019-09-12 models/transformer.py
Concat mean and max pooling instead of only mean

@@ -61,7 +61,7 @@ class BertImage(nn.Module):
         # self.features_downscale = nn.Linear(self.hidden_size, num_channels_in)
 
         self.encoder = BertEncoder(bert_config)
-        self.classifier = nn.Linear(self.hidden_size, num_classes)
+        self.classifier = nn.Linear(self.hidden_size * 2, num_classes)
         # self.pixelizer = nn.Linear(self.hidden_size, 3)
         self.register_buffer("attention_mask", torch.tensor(1.0))
 
@@ -183,8 +183,13 @@ class BertImage(nn.Module):
                 output_all_encoded_layers=False,  # TODO
             )[0]
 
+        # Pooling: concatenate mean and max pooling
         # mean pool for representation (features for classification)
-        cls_representation = representations.view(b, -1, representations.shape[-1]).mean(dim=1)
+        cls_representation = torch.cat([
+            representations.view(b, -1, representations.shape[-1]).mean(dim=1),
+            representations.view(b, -1, representations.shape[-1]).max(dim=1)[0]
+        ], dim=1)
+
         cls_prediction = self.classifier(cls_representation)
 
         return cls_prediction
